\documentclass{beamer}

% Theme choice:
\usetheme{CambridgeUS}

% Title page details: 
\title{Hospital Management System} 
\begin{document}

% Title page frame
\begin{frame}
    \titlepage 
\end{frame}

% Remove logo from the next slides
\logo{}


% Outline frame
\begin{frame}{Roles in Application}
    \tableofcontents
\end{frame}

\begin{frame}{LOGIN PAGE}
	\begin{itemize}
	\item Login ID :
	\item Password :
	\end{itemize}
For Emergency: \underline{\textbf{CLICK HERE}}
\end{frame}

\begin{frame}{EMERGENCY}
Enter the following credentials:
\begin{itemize}
\item \textbf{Name :}
\item \textbf{Age :}
\item \textbf{Gender :}
\item \textbf{Phone Number :}
\item \textbf{Adhaar Number :}
\end{itemize}
Click \textbf{OK} to register (This redirects to Book Appointment Page,\\
	where, they select specific doctor of that particular emergency).
\end{frame}


% Lists frame
\section{Admin}
\begin{frame}{Admin}
Roles of Admin:
\begin{itemize}
    \item Add New Patient(extra subtopic: Emergency candidates) 
    \item Edit Patient information
    \item Add Doctors
    \item Edit Doctor Details
    \item Medicines Information (Availability etc)
    \item Add Donated items and information
    \item Availability of Donated items.
\end{itemize}

\end{frame}
%
\begin{frame}{Admin : i) Add New Patient}
\underline{\textbf{Sub Topics:}}
\begin{itemize}
\item \textbf{Name :}
\item \textbf{Age :}
\item \textbf{Gender :}
\item \textbf{Phone Number :}
\item \textbf{Adhaar Number :}
\end{itemize}
“Now This Auto Generates Login ID and Password of Patient should be entered.”\\
Enter Password:\\
Eg: ID:Patient1 Password:1patient.
\end{frame}
%
\begin{frame}{Admin : ii) Edit Patient Information}
\begin{itemize}
\item Age :
\item Phone Number :
\end{itemize}
i.e.,\\[12pt]
"Admin can only change Age and Phone number of the patient,\\
Name,Gender,etc can't be changed once entered.
\end{frame}
%
\begin{frame}{Admin : iii) Add Doctors}
\begin{itemize}
\item \textbf{Name :}
\item \textbf{Phone Number :}
\item \textbf{Gender :}
\item \textbf{Specialization :}
\item \textbf{Initializing Time Slot :} (eg: 8hrs [10am - 6pm]).
\end{itemize}
Later, Admin can change Doctors Time Slot as per Hospital instructions.
\end{frame}
%
\begin{frame}{Admin : iv) Edit Doctor Details}
\begin{itemize}
\item Phone Number:
\item Time Slots:
\item Remove Doctor : "Enter Name of Doctor".
\end{itemize}
\end{frame}
%
\begin{frame}{Admin : v) Medicine Information}
\begin{itemize}
\item Add Medicine.(need to add number of months validity)
\item View Existing Medicines {“Display all the list of medicines"}.
"Medicines auto removed after expiry."
\end{itemize}
\end{frame}
%
\begin{frame}{vi) Adding Donated items and information}
\begin{itemize}
\item Enter Item Name(eg. Heart,Kidney) and Donated by( Name of Person, Phone Number and other Details)
\end{itemize}
\end{frame}
%
\begin{frame}{vii) Availability of Donated items.}
\begin{itemize}
\item Displays List of Items and their quantity.
\end{itemize}
Eg: Heart and Number of Hearts = 2.
\end{frame}
\section{Patient}
\begin{frame}{Patient}
\underline{\textbf{Sub Topics :}}
\begin{itemize}
\item Book Appointment.\\
"After Booking, Patient name and his disease will be displayed to doctor under his Page".
\item View Previous Details (includes Test Reports and Medicine Lists etc)
\end{itemize}
\end{frame}
%
\begin{frame}{Patient : i)Book Appointment}
\begin{block}{1) General Appointment (Regular Checkup):}
\begin{itemize}
\item "Display List of General Doctors and their Timeslots".
\end{itemize}
\end{block}
\begin{block}{2) Specialized Appointment (Particular Disease Treatment purpose):}
\begin{itemize}
\item "Enter the specialization required (based on disease): "
\begin{itemize}
\item "Display List of Specialized Doctors and their Timeslots".
\end{itemize}
\end{itemize}
\end{block}
\end{frame}
%
\begin{frame} {Patient : ii)View Previous Details}
\begin{exampleblock}{Display List}
 ”List of (Doctor Name , Disease , Medicine slip , Test Reports)”
\end{exampleblock}
and \\[40pt]
(optional thing) : If Room Allocated, (Add Discharging Option).
\end{frame}
%
\section{Doctor}
\begin{frame}{Doctor}
\underline{\textbf{Sub Topics:}}
\begin{itemize}
\item List of Active Patients under him:\\[6pt]
"Patient Name, Age ,Gender"\\[10pt]
\textbf{Doctor} should add:
\begin{itemize}
\item Disease Details
\item Medicines
\item Tests (adds Test report files if required)
\item Room Allocation\\
(None if not required, else need to select Room number Displayed)
\end{itemize}
\end{itemize}
\begin{exampleblock}{Display}
 Display His Working Time slots of the Day.
\end{exampleblock}
\end{frame}
\begin{frame}
\begin{center}
\begin{large}
\textbf{THANK YOU}
\end{large}
\end{center}
\begin{itemize}
\item Bindusree
\item Sai Vamsi
\item Pranav Varma 
\end{itemize}
\end{frame}
\end{document}